Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-08 tex/ms.tex
more discussion text and figure list

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$, 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines.

@@

@@

BDJ INSERT WORDS HERE.  We have shown that we can combine photometric
and spectroscopic data in a principled way to infer physical
properties.  We do not resort to an arbitrary down-weighting or
up-weighting of certain data. Instead, we explicitly model our
uncertainty in the spectral calibration.  This combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration for a number of applications.  Furthermore, our strategy
easily extensible to more complicated models, which include for
example night sky line emission in the spectroscopy, wavelength
calibration.

>>>>

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$, 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines. 
This is the mean model which appears in equation
\ref{eq:SpectroscopicLF}.

@@

\begin{figure}[h!]
\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
\end{figure}

@@

BDJ INSERT WORDS HERE.  We have demonstrated that we can combine
photometric and spectroscopic data in a principled way to infer
physical properties.  We do not resort to an arbitrary down-weighting
or up-weighting of certain data. Instead, we explicitly model our
uncertain knowledge of the spectral calibration.  For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration.  Calibration information,
if it exists, can be used to generate informative priors on the
calibration parameters of our model. Furthermore, our strategy is
easily extensible to more complicated models, which include for
example night sky line emission in the spectroscopy, wavelength
calibration.

In a heirarchical model it should be possible to use the inferred
calibration parameters, along with additional information about the
observations (e.g. airmass, instrument temperature), to in turn infer
the parameters of a generative model for the calibration.

Limitations.  The strategy we have outlined here has several
limitations.  First, it requires a generative model for the spectrum of
the object of interest, and is thus ill-suited to discovery projects.
